The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
inc more mlnet indiv fitness perspective

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Social phenotypes are
increasingly linked to important fitness for individuals of various species,
including primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both temporal, seasons
and stages of life, and social scales, types of interactions, have emerged as
important for understanding fitness consequences in the context of social
network positions [@Almeling_2016, @Berger_2015, @Brent_2017, @Holekamp_2012].
Multilayer networks provide a way to bridge these different scales so that we
can examine social phenotypes in more holistic ways rather than looking at each
scale separately as has traditionally been done.

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015] With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the summer **check**,
individuals demonstrate dramatically different graph strength **cite spatial threshold fig** 
in different habitat types, having dramatically higher graph
strength in forage and open habitats than forest where they can likely see each
other better and still interact with visual cues. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) 
had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences.

Temporal scale is also important for understanding the repercussions of social
phenotypes. Varying the time window length and position for caribou, we found
there was a lot of variation in the multilayer network metrics **cite winpos and winlen**. 
These changes in the outcome depending on how the time window is
defined highlight how critical it is to properly define the time window
appropriately to address the questions and hypotheses of interest. For instance,
social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
temporal scale that is meaningful for the proposed hypotheses. Further
complicating the issue of selecting suitable time scales across ontogeny,
individuals progress through development at different rates [@Tarka_2018]. This
variation can make defining appropriate temporal scales for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny even more difficult when they vary by individual. However, considering
fine temporal scales provide insight across developmental stages that may
otherwise be missed [@Turner_2018].

>>>>

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales so that we can examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017,
@Holekamp_2012].

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015] With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the summer **check**,
individuals demonstrate dramatically different graph strength **cite spatial threshold fig**
in different habitat types, having higher graph strength in
forage and open habitats where they can likely see each other and still interact
with visual cues than in forest habitats. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca
mulatta*) had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences. Multilayer networks provide the opportunity to
address these types of questions involving social scale with all the individual
layers of interaction integrated in a holistic way.

Temporal scale is also important for understanding the repercussions of social
phenotypes. Varying the time window length and position for caribou, we found
there was a lot of variation in the multilayer network metrics **cite winpos and winlen**. 
These changes in the outcome depending on how the time window is
defined highlight how critical it is to properly define the time window
appropriately to address the questions and hypotheses of interest. For instance,
social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
temporal scale that is meaningful for the proposed hypotheses. Further
complicating the issue of selecting suitable time scales across ontogeny,
individuals progress through development at different rates [@Tarka_2018]. This
variation can make defining appropriate temporal scales for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny even more difficult when they vary by individual. However, considering
fine temporal scales provide insight across developmental stages that may
otherwise be missed [@Turner_2018]. Defining temporal scales is a challenge in
multilayer networks just as in monolayer networks; however, multilayer networks
provide metrics that enable researchers to look at similarities and differences
in separate layers representing different stages of ontogeny, or seasons as in
our case study, which can be difficult to detect.
